---
title: "Test averages separating diversity pi and He"
author: "| Moi Exposito-Alonso\n| \n| Department of Integrative Biology, University
  of California Berkeley, California, USA\n| Howard Hughes Medical Institute, University
  of California Berkeley, California, USA\n| \n| Correspondance: moisesexpositoalonso@gmail.com\n"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    # toc: yes
    # toc_depth: 3
    latex_engine: xelatex
    fig_caption: yes
fontsize: 10pt
mainfont: Times New Roman
indent: no
# header-includes:
#   - \usepackage{etoolbox}
#   - \usepackage{tocloft}
#   - \usepackage{caption}
#   - \renewcommand{\contentsname}{List of Texts}
#   - \pretocmd{\caption}{\addcontentsline{toc}{section}{\protect\numberline{\thefigure}#1}}{}{}
#   - \renewcommand{\figurename}{Figure S}
#   - \renewcommand{\tablename}{Table S}
#   - \pretocmd{\caption}{\addcontentsline{lot}{table}{\protect\numberline{\thetable}#1}}{}{}
---

```{r setup, warning=F, echo=F, include=FALSE}
mypath<-"~/extinction/Response-GenDivMetaAnalysis/"
setwd(mypath)
knitr::opts_knit$set(root.dir = mypath)

# Dadta
library(dplyr)
library(tidyr)

# Tables
library(dplyr)
library(knitr)
library(kableExtra)
require(stringr)

# Models
library(MCMCglmm)

# Plots
library(latex2exp)
library(scales)
library(ggplot2)
library(RColorBrewer)
library(ggside)
library(cowplot)

library(ggplot2)

library(showtext)


source("Response-functions.R")

```

```{r read_data, echo=FALSE, eval=TRUE, warning=FALSE}
dfheci<-read.csv("tmp/dfheci.csv")
dfpionlyci<-read.csv("tmp/dfpionlyci.csv")
```

*For diversity* $H_e$\ 

Arithmetic mean Hedge's g = `r printmean(dfheci$HedgesG)` ±`r printCI(dfheci$HedgesG)` (95% CI).\
Weighted SE mean Hedge's g = `r clean(metaztest(dfheci$HedgesG,dfheci$HedgesG.err)$Weighted_mean)` ± `r clean(metaztest(dfheci$HedgesG,dfheci$HedgesG.err)$CI_half_width)`(95% CI).\
MCMCglmm mean (intercept) of Hedge's g = `r posteriormcmc(metamcmc(dfheci, variable="HedgesG", se="HedgesG.err", random_effects=c("PaperID","Binomen.rotl") ))$summary` .


Arithmetic mean % $\pi$ = `r printmean(dfheci$Percent.Change)`% ± `r printCI(dfheci$Percent.Change)`% (95% CI).\
Weighted SE mean % $\pi$ = `r clean(metaztest(dfheci$Percent.Change,dfheci$SE.Percent.Change)$Weighted_mean)`% ± `r clean(metaztest(dfheci$Percent.Change,dfheci$SE.Percent.Change)$CI_half_width)`% (95% CI).\
MCMCglmm mean (intercept) of % $\pi$ = `r posteriormcmc(metamcmc(dfheci, variable="SE.Percent.Change.delta", se="SE.Percent.Change.delta",random_effects=c("PaperID","Binomen.rotl")))$summary` .

Geometric mean % $\pi$ = `r printmean((exp(mean(dfheci$Log.Change)) - 1) * 100)`% ± `r clean((exp(printCI(dfheci$Log.Change)) - 1) * 100)`% (95% CI).\
Geometric Weighted SE mean % $\pi$ = `r clean((exp(mean(metaztest(dfheci$Log.Change, dfheci$SE.Log.Change)$Weighted_mean)) - 1) * 100)`% ± `r clean((exp(mean(metaztest(dfheci$Log.Change, dfheci$SE.Log.Change)$CI_half_width)) - 1) * 100)`% (95% CI).\
Geometric MCMCglmm mean $\pi$ = `r 100*(exp(posteriormcmc(metamcmc(dfheci, variable="Log.Change", se="SE.Log.Change", random_effects=c("PaperID","Binomen.rotl") ))$center)-1 )`% 
± `r 100*(exp(posteriormcmc(metamcmc(dfheci, variable="Log.Change", se="SE.Log.Change", random_effects=c("PaperID","Binomen.rotl") ))$hpi_half_width)-1 )`% (95% CI)

*For diversity* $\pi$\

Arithmetic mean Hedge's g = `r printmean(dfpionlyci$HedgesG)` ±`r printCI(dfpionlyci$HedgesG)` (95% CI).\
Weighted SE mean Hedge's g = `r clean(metaztest(dfpionlyci$HedgesG,dfpionlyci$HedgesG.err)$Weighted_mean)` ± `r clean(metaztest(dfpionlyci$HedgesG,dfpionlyci$HedgesG.err)$CI_half_width)`(95% CI).\
MCMCglmm mean (intercept) of Hedge's g = `r posteriormcmc(metamcmc(dfpionlyci, variable="HedgesG", se="HedgesG.err", random_effects=c("PaperID","Binomen.rotl") ))$summary` .


Arithmetic mean % $H_e$ = `r printmean(dfpionlyci$Percent.Change)`% ± `r printCI(dfpionlyci$Percent.Change)`% (95% CI).\
Weighted SE mean % $H_e$ = `r clean(metaztest(dfpionlyci$Percent.Change,dfpionlyci$SE.Percent.Change)$Weighted_mean)`% ± `r clean(metaztest(dfpionlyci$Percent.Change,dfpionlyci$SE.Percent.Change)$CI_half_width)`% (95% CI).\
MCMCglmm mean (intercept) of % $H_e$ = `r posteriormcmc(metamcmc(dfpionlyci, variable="SE.Percent.Change.delta", se="SE.Percent.Change.delta",random_effects=c("PaperID","Binomen.rotl")))$summary` .

Geometric mean % $H_e$ = `r printmean((exp(mean(dfpionlyci$Log.Change)) - 1) * 100)`% ± `r clean((exp(printCI(dfpionlyci$Log.Change)) - 1) * 100)`% (95% CI).\
Geometric Weighted SE mean % $H_e$ = `r clean((exp(mean(metaztest(dfpionlyci$Log.Change, dfpionlyci$SE.Log.Change)$Weighted_mean)) - 1) * 100)`% ± `r clean((exp(mean(metaztest(dfpionlyci$Log.Change, dfpionlyci$SE.Log.Change)$CI_half_width)) - 1) * 100)`% (95% CI).\
Geometric MCMCglmm mean $H_e$ = `r 100*(exp(posteriormcmc(metamcmc(dfpionlyci, variable="Log.Change", se="SE.Log.Change", random_effects=c("PaperID","Binomen.rotl") ))$center)-1 )`% 
± `r 100*(exp(posteriormcmc(metamcmc(dfpionlyci, variable="Log.Change", se="SE.Log.Change", random_effects=c("PaperID","Binomen.rotl") ))$hpi_half_width)-1 )`% (95% CI)

